05-applying_lime

### 2019-02-22 journals/05-applying_lime.Rmd
added more descriptions to journal 05

It applies LIME using my function `run_lime` specify the different input values and save the output from the `lime` function and the `explain` function in two lists. The `lime` and `explain` outputs and the input settings are saved as .rds files.

@@

This code combines the test data and the explanations.

@@

This code creates a dataset with summaries of the explanations.

@@

@@

It applies LIME using my function `run_lime` specify the different input values and save the output from the `lime` function and the `explain` function in two lists. The `lime` and `explain` outputs and the input settings are saved as .rds files.

@@

```{r}
# Join the sensativity outputs with the test data
hamby224_sensitivity_joined <- hamby224_sensitivity_outputs %>%
  full_join(hamby224_test %>% na.omit() %>% 
                mutate(case = as.character(case)), by = "case") %>%
    mutate(case = factor(case)) %>%
    select(case, model_r2:feature_weight, bin_continuous:rep, 
           set:land2, rfscore, samesource) %>%
    mutate(diff = rfscore - model_prediction,
         nbins = as.numeric(as.character(nbins)),
         situation = ifelse(bin_continuous == TRUE & bin_method == "quantile_bins", 
                            sprintf("%.0f quantile", nbins),
                            ifelse(bin_continuous == TRUE & bin_method == "equally_spaced",
                                   sprintf("%.0f equally spaced", nbins),
                                   ifelse(bin_continuous == TRUE & bin_method == "tree" &
                                            response == "samesource",
                                          sprintf("%.0f samesource tree", nbins),
                                          ifelse(bin_continuous == TRUE & bin_method == "tree" &
                                            response == "rfscore",
                                            sprintf("%.0f rfscore tree", nbins),
                                            ifelse(bin_continuous == FALSE & 
                                                   use_density == TRUE, 
                                                   "kernel density", 
                                                   "normal approximation"))))) %>%
           fct_relevel("2 quantile", "3 quantile", "4 quantile",
                       "5 quantile", "6 quantile", "2 equally spaced",
                       "3 equally spaced", "4 equally spaced",
                       "5 equally spaced", "6 equally spaced",
                       "2 samesource tree", "3 samesource tree",
                       "4 samesource tree", "5 samesource tree",
                       "6 samesource tree")) %>%
    mutate(bin_situation = ifelse(bin_method == "quantile_bins" & 
                                  bin_continuous == TRUE,
                                  "quantile",
                                  ifelse(bin_method == "equally_spaced" & 
                                         bin_continuous == TRUE,
                                         "equally spaced", 
                                         ifelse(bin_method == "tree" & 
                                                bin_continuous == TRUE & 
                                                response == "samesource",
                                                "samesource tree", 
                                                ifelse(bin_method == "tree" & 
                                                       bin_continuous == TRUE & 
                                                       response == "rfscore",
                                                       "rfscore tree", 
                                                       ifelse(bin_continuous == FALSE & 
                                                       use_density == TRUE, 
                                                       "kernel density", 
                                                       "normal approximation")))))) %>%
    mutate(bin_situation = factor(bin_situation))

write.csv(hamby224_sensitivity_joined, "../data/hamby224_sensitivity_joined.csv",
          row.names = FALSE)
```

>>>>

It applies LIME using my function `run_lime` to specify the different input values. The outputs from the `lime` function are combined into a list, and the outputs from the `explain` function are combined into dataframe. Both are saved as .rds files.

@@

This code combines the test data and the LIME explanations into one dataframe and saves the dataframe.

@@

This code creates and saves a dataset with summaries of the explanations.

@@

I was interested in determining how the random permutations affect ths results from LIME. That is, I wanted to do a sensativity analysis. The code below applies the LIME algorithm to the bullet data ten times for each of the following different input cases:

@@

It applies LIME using my function `run_lime` to specify the different input values. The outputs from the `explain` function are combined into a dataframe and saved as .rds file. The input values are also saved as an .rds file.

@@

The code below joins the sensativity outputs with the test data into a dataframe. The dataframe is saved as an .rds file.

```{r}
# Join the sensativity outputs with the test data if not already saved
if(!file.exists("../data/hamby224_sensitivity_joined.rds")) {

hamby224_sensitivity_joined <- hamby224_sensitivity_outputs %>%
  full_join(hamby224_test %>% na.omit() %>% 
                mutate(case = as.character(case)), by = "case") %>%
    mutate(case = factor(case)) %>%
    select(case, model_r2:feature_weight, bin_continuous:rep, 
           set:land2, rfscore, samesource) %>%
    mutate(diff = rfscore - model_prediction,
         nbins = as.numeric(as.character(nbins)),
         situation = ifelse(bin_continuous == TRUE & bin_method == "quantile_bins", 
                            sprintf("%.0f quantile", nbins),
                            ifelse(bin_continuous == TRUE & bin_method == "equally_spaced",
                                   sprintf("%.0f equally spaced", nbins),
                                   ifelse(bin_continuous == TRUE & bin_method == "tree" &
                                            response == "samesource",
                                          sprintf("%.0f samesource tree", nbins),
                                          ifelse(bin_continuous == TRUE & bin_method == "tree" &
                                            response == "rfscore",
                                            sprintf("%.0f rfscore tree", nbins),
                                            ifelse(bin_continuous == FALSE & 
                                                   use_density == TRUE, 
                                                   "kernel density", 
                                                   "normal approximation"))))) %>%
           fct_relevel("2 quantile", "3 quantile", "4 quantile",
                       "5 quantile", "6 quantile", "2 equally spaced",
                       "3 equally spaced", "4 equally spaced",
                       "5 equally spaced", "6 equally spaced",
                       "2 samesource tree", "3 samesource tree",
                       "4 samesource tree", "5 samesource tree",
                       "6 samesource tree")) %>%
    mutate(bin_situation = ifelse(bin_method == "quantile_bins" & 
                                  bin_continuous == TRUE,
                                  "quantile",
                                  ifelse(bin_method == "equally_spaced" & 
                                         bin_continuous == TRUE,
                                         "equally spaced", 
                                         ifelse(bin_method == "tree" & 
                                                bin_continuous == TRUE & 
                                                response == "samesource",
                                                "samesource tree", 
                                                ifelse(bin_method == "tree" & 
                                                       bin_continuous == TRUE & 
                                                       response == "rfscore",
                                                       "rfscore tree", 
                                                       ifelse(bin_continuous == FALSE & 
                                                       use_density == TRUE, 
                                                       "kernel density", 
                                                       "normal approximation")))))) %>%
    mutate(bin_situation = factor(bin_situation))

  # Save the joined test and explained dataframes
  saveRDS(hamby224_sensitivity_joined, "../data/hamby224_sensitivity_joined.rds")

  # Load in the sensitivity inputs and outputs
  hamby224_sensitivity_joined <- readRDS("../data/hamby224_sensitivity_joined.rds")
